{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-07-19 sftrends_manu.Rnw
tracy plot finished, h2dat added

source('R/funcs.r')
library(WRTDStidal)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(purrr)
library(tidyr)
library(Hmisc)
@

@@

@@

# globals
ylab <- expression(paste('DIN (mg ', L^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank()
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Set1')[c(3, 2, 1)]
col_lim <- c(0, 3.8)
xlims <- range(toplo$date)
txt <- data.frame(
  x = min(toplo$date), 
  y =  c(5, 2.4, 0.5, 7), 
  txt = c('a', 'b', 'c', 'd')
)
size <- 7

@@

<<tracy, fig.height = 5, fig.width = 8, out.width = '\\textwidth', fig.cap = 'test'>>=
data(potw_load)

@@

p1 <- ggplot(toplo1, aes(x = date, y = val)) + 
  geom_line(colour = lncol) + 
  scale_x_date(expand = c(0, 0)) + 
  scale_y_continuous(ylab, expand = c(0, 0), limits = c(50, 850)) + 
  ptheme

p2 <- ggplot(toplo2, aes(x = date, y = val, group = var, fill = var)) + 
  geom_area(stat = 'identity', position = 'fill') + 
  scale_x_date(expand = c(0, 0)) + 
  scale_fill_brewer(palette = 'Blues', labels = leglabs) + 
  scale_y_continuous('% of total nitrogen', expand = c(0, 0)) + 
  ptheme + 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
    )

>>>>

source('R/funcs.r')
library(WRTDStidal)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(purrr)
library(tidyr)
library(Hmisc)
library(ggrepel)
@

@@

Overall reduction in total nitrogen load was observed as a result of reduction in ammonium (\cref{fig:tracy}).  Nitrate is the primary constituent of total nitrogen after 2007.

@@

# globals
ylab <- expression(paste('DIN (mg ', L^-1, ')'))
ptheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    axis.title.x = element_blank()
  )
col_vec <- RColorBrewer::brewer.pal(9, 'Set1')[c(3, 2, 1)]
col_lim <- c(0, 3.8)
xlims <- range(toplo$date)
txt <- data.frame(
  x = max(toplo$date), 
  y =  c(5, 2.4, 0.5, 7), 
  txt = c('(a)', '(b)', '(c)', '(d)')
)
size <- 7

@@

<<tracy, fig.height = 5, fig.width = 8, out.width = '\\textwidth', fig.cap = 'Nitrogen load measurements (kg d$^{-1}$) at the City of Tracy Wastewater Treatment Plant, San Joaquin County.  Wastewater discharge requirements were implemented in May, 2007 to include nitrification/denitrification and tertiary filtration causing a reduction in total nitrogen effluent discharged to the Delta. Reductions were primarily observed for ammonium.'>>=
data(potw_load)

@@

lndate <- as.Date('2007/05/01')

p1 <- ggplot(toplo1) + 
  geom_line(colour = lncol, aes(x = date, y = val)) + 
  scale_x_date(expand = c(0, 0)) + 
  scale_y_continuous(ylab, expand = c(0, 0), limits = c(50, 850)) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  geom_label_repel(
    data = data.frame(x = lndate, y = 600), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) + 
  ptheme

p2 <- ggplot(toplo2, aes(x = date, y = val, group = var, fill = var)) + 
  geom_area(stat = 'identity', position = 'fill') + 
  scale_x_date(expand = c(0, 0)) + 
  scale_fill_brewer(palette = 'Blues', labels = leglabs) + 
  scale_y_continuous('% of total nitrogen', expand = c(0, 0)) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  ptheme + 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
    )

### 2016-07-19 sftrends_manu.tex
update clams plot with biomass flow reg
load figure for tracy, needs caption
tracy plot finished, h2dat added

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Wed Jul 13 15:18:11 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\subsubsection{Clam invasion in Suisun Bay}

@@

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, David Senn$^2$, Phil Bresnahan$^2$, Emily Novick$^2$, James D. Hagy III$^1$,}}
  \\{\bf {\normalsize Thomas Jabusch$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:hagy.jim@epa.gov}{hagy.jim@epa.gov}}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Avenue, Richmond, CA 94804}}
	\\{\textit {\normalsize Phone: 510-746-7334, Fax: 510-746-7300}}
	\\{\textit {\normalsize Emails: \href{mailto:davids@sfei.org}{davids@sfei.org}, \href{mailto:philb@sfei.org}{philb@sfei.org}, \href{mailto:emilyn@sfei.org}{emilyn@sfei.org}, \href{mailto:thomasj@sfei.org}{thomasj@sfei.org}}}
  \vspace{1in} 
  \\ Version Date:   Mon Jul 18 18:28:15 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\subsubsection{Effects of wastewater treatment}

Overall reduction in total nitrogen load was observed as a result of reduction in ammonium (\cref{fig:tracy}).  Nitrate is the primary constituent of total nitrogen after 2007.

\subsubsection{Effects of biological invasions}

@@

{\centering \includegraphics[width=\textwidth]{figs/tracy-1}

\caption[Nitrogen load measurements (kg d]{Nitrogen load measurements (kg d$^{-1}$) at the City of Tracy Wastewater Treatment Plant, San Joaquin County.  Wastewater discharge requirements were implemented in May, 2007 to include nitrification/denitrification and tertiary filtration causing a reduction in total nitrogen effluent discharged to the Delta. Reductions were primarily observed for ammonium.}\label{fig:tracy}
\end{figure}
